---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
options( stringsAsFactors = FALSE
       , tidyverse.quiet = TRUE
       )
library(knitr)
library(printr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# cursory

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/halpo/cursory.svg?branch=master)](https://travis-ci.org/halpo/cursory)
[![Codecov test coverage](https://codecov.io/gh/halpo/cursory/branch/master/graph/badge.svg)](https://codecov.io/gh/halpo/cursory?branch=master)
<!-- badges: end -->

The goal of cursory is to make it easier to summarise data and look
at your variables.  It builds off [`dplyr`](http://dplyr.tidyverse.org) 
and [`purrr`](http://purrr.tidyverse.org).  It is also compatible with 
[`dbplyr`](http://dbplyr.tidyverse.org) and remote data.

## Installation

You can install the released version of cursory from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("cursory")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("halpo/cursory")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dplyr)
library(cursory)
data(iris)

## basic summary statistics for each variable in a data frame.
cursory_all(group_by(iris, Species), lst(mean, sd)) %>% ungroup() 

## summary statistics for only numeric variables. 
cursory_if(iris, is.numeric, lst(Mean = mean, 'Std.Dev.' = sd))

## summary statistics for specific variables. 
cursory_at(iris, vars(ends_with("Length")), var)
```

